Supporting Information

### 2018-03-08 SupportingInformation.Rmd
put the mtime function in its own file

#A function needed for caching
mtime <- function(files)
{
  lapply(Sys.glob(files),function(x) X =   
          file.info(x)$mtime)
}

source("getcopula.R")
source("OurBiCopSelect.R")
source("FittingCopula_selective_loc.R")
source("aphid_data_calling.R")
source("plankton_north_sea_data_calling.R")
source("NonParamStat.R")
source("copsurrog2d.R")
source("TestStats_multivar_dataset.R")
source("skewness_multivar_dataset.R")
```

>>>>

source("mtime.R") #A function needed for caching
source("getcopula.R")
source("OurBiCopSelect.R")
source("FittingCopula_selective_loc.R")
source("aphid_data_calling.R")
source("plankton_north_sea_data_calling.R")
source("NonParamStat.R")
source("copsurrog2d.R")
source("TestStats_multivar_dataset.R")
source("skewness_multivar_dataset.R")
```
